---
title: "R_Mini_Project"
author: "Hennie Bezuidenhout"
date: "06 September 2016"
output: word_document
---
# Call packages to accomodate Project
```{r}
library(readr)
library(tidyr)
library(dplyr)
library(lubridate)
library(knitr)
library(ggplot2)
```
# Append data files 
```{r}
eqs_frame <- list.files(path = "G:/Hennie/R Studio/Project Data/First R Project", full.names = TRUE) %>%
  lapply(read_csv) %>%
  bind_rows()

```

# Filter Data to return Top 20 Market Cap Stocks for each month
```{r}
Top20 <- eqs_frame %>%
  group_by(date) %>%
  arrange (desc(MarketCapUSD)) %>%
  filter(!is.na(MarketCapUSD)) %>%
  slice (1:20) %>%
  ungroup() %>% 
  select (date, Ticker, MarketCapUSD)

```

# Provide a Table to outline results for January
```{r}
Top20_Jan <- filter(Top20,date == "2016-01-31")
kable(Top20_Jan, digits =1, caption = "Top 20 Market Cap Stocks: January")

```
# Calculating and outlining z-score for January
```{r}
zscore_eqs <- eqs_frame %>%
group_by(date) %>%
mutate (z_score = (BookYield - mean(BookYield, na.rm = TRUE))/sd(BookYield, na.rm = TRUE))


zscore_jan <- zscore_eqs %>%
filter(date == "2016-01-31") %>%
arrange(desc(z_score)) %>%
select (date,Ticker, z_score) 
kable(zscore_jan, digits = 2, caption = "All January Stocks ranked by Z-Score")

```

# Grouping Book Yield Z Score by month and filter to reveal Top 10 across the respective months
```{r}
zscore_group <- zscore_eqs %>%
  group_by(date) %>%
  arrange (desc(z_score)) %>%
  filter(!is.na(z_score)) %>%
  slice(1:10) %>%
  ungroup() %>%
  select(date, Ticker, MarketCapUSD, EarningsYield, z_score)
  kable (zscore_group, digits = 2, caption = "Monthly Top 10 z-score stocks")

```

# Calculate the Market Cap weighted weight across the 3 months (USD market caps used for entire data set)
```{r}

cap_weighted <- eqs_frame %>%
  group_by(date) %>%
  mutate(weight = MarketCapUSD/sum(MarketCapUSD)) %>%
  ungroup()

```
# Calculate the EarningsYield for each Cap-Weighted portfolio
```{r}
earnings_capweighted <- cap_weighted %>%
  group_by(date) %>%
  mutate(ey_weights = EarningsYield * weight) %>%
  ungroup()
```
# Filter data set across months to calculate EY per month
```{r}
ey_jan <- filter(earnings_capweighted, date =="2016-01-31")
summarise(ey_jan, jan_ey = sum(ey_weights, na.rm = TRUE))

ey_feb <- filter(earnings_capweighted, date =="2016-02-29")
summarise(ey_feb, feb_ey = sum(ey_weights, na.rm = TRUE))

ey_mar <- filter(earnings_capweighted, date =="2016-03-31")
summarise(ey_mar, mar_ey = sum(ey_weights, na.rm = TRUE))

```
# Plot Z_Scores for January: Bar Chart
```{r}
janeqs <- filter(zscore_eqs, date =="2016-01-31")
ggplot(janeqs, aes(x = Ticker, y = z_score)) +
  geom_bar(stat = "identity") +
  theme(axis.text.x=element_blank(), 
        axis.ticks.x=element_blank())

```
# Plot Earnings Yield for Cap Weighted Portfolio Stocks: Time-Series Chart
```{r}

ggplot(earnings_capweighted, aes(x = date, y = EarningsYield)) +
  geom_line(aes(color = Ticker), size = 0.30, show.legend = FALSE)

```








